Effects of pre-existing structures on the seismicity of the Charlevoix Seismic Zone

### 2019-06-27 main_full_manuscript.tex
Updated

\section{Introduction}
The Charlevoix Seismic Zone (CSZ) is the most seismically active region in eastern Canada. The CSZ is within the \change[OF]{Cambro-Ordovician}{Late Precambrian} St. Lawrence rift zone in southeastern Quebec and is overprinted by a Devonian impact \change[OF]{crater}{structure} (Fig. \ref{figone}). The impact \change[OF]{crater}{structure} has a radius of 28 km and is \change[OF]{15}{approximately 12} km deep~\citep{RONDOT1994}. The \change[OF]{crater}{impact structure} has a more damaged interior zone with a surface radius of 18 km (Fig. \ref{figone}). The impact \change[OF]{crater}{structure} is superimposed on three major rift faults trending N35$^\circ$E and dipping to the southeast~\citep{anglin1984,Rondot_1971}. The CSZ \change[OF]{is considered to pose a high risk of seismic hazard}{has high risk of seismic hazards} due to its history of generating \change[OF]{large}{moderate to large} earthquakes \citep{anglin1984,lamontagne1999}. Over 200 earthquakes are recorded each year in the CSZ (Nuttli magnitude, mN \add[OF]{mostly} $\leq$ 3) \citep{Baird_2010} and the hypocenters have a bimodal distribution with peaks at 10 and 22 km depths \citep{Vlahovic_2003}. The vast majority of earthquakes in the CSZ occur within the volume bounded by the rift faults \citep{Yu_2016} and those with greater magnitudes occur northeast of the \change[OF]{crater}{impact structure}~\citep{Mazzotti_2010} (Fig. \ref{figone}).

\begin{figure}[h]
\centering
\includegraphics[width=18.5pc]{Figures/Map_of_CSZ_2.png} 
\caption{Topography\add[OF]{, bathymetry,} and seismicity of the Charlevoix Seismic Zone (CSZ) as well as the locations of the impact \change[OF]{crater}{structure} (outer cyan circle) and the more damaged inner \change[OF]{crater}{impact structure} (inner cyan circle). Small circles \add[OF]{and diamonds} are the relocated epicenters~\citep{Powell_2017} \add[OF]{and the complete dataset for the years 1988-2011, respectively,} and their colors represent the focal depths. The focal mechanisms are for the earthquakes used by \citet{Mazzotti_2010} for the stress inversion. Large circles labeled as NW and SE show orientations of SH$_{\max}$ from the stress inversion of focal mechanism (SH$_S$) and from borehole breakout measurements (SH$_B$) for the earthquake clusters northwest and southeast of the \change[OF]{crater}{impact structure} center. Solid black lines mark the rift faults known in the region: GNF, Gouffre Northwest Fault; SLF, Saint-Laurent fault; CHF, Charlevoix Fault; and SSF, South Shore Fault \citep{Rondot_1971,lamontagne1999}. The inset shows the location of the CSZ in eastern Canada. Earthquake \change[OF]{epicenters}{hypocenters} from the National Resources Canada catalog for the years 1988-2011.}
\label{figone}
\end{figure}

>>>>

\section{Introduction}
The Charlevoix Seismic Zone (CSZ) is the most seismically active region in eastern Canada. The CSZ is within the \change[OF]{Cambro-Ordovician}{Late Precambrian} St. Lawrence rift zone in southeastern Quebec and is overprinted by a Devonian impact \change[OF]{crater}{structure} (Fig. \ref{figone}). The impact \change[OF]{crater}{structure} has a radius of 28 km and is \change[OF]{15}{approximately 12} km deep~\citep{RONDOT1994}. The \change[OF]{crater}{impact structure} has a more damaged interior zone with a surface radius of 18 km (Fig. \ref{figone}). The impact \change[OF]{crater}{structure} is superimposed on three major rift faults trending N35$^\circ$E and dipping to the southeast~\citep{anglin1984,Rondot_1971}. The CSZ \change[OF]{is considered to pose a high risk of seismic hazard}{has a high seismic hazards} due to its history of generating \change[OF]{large}{moderate to large} earthquakes \citep{anglin1984,lamontagne1999}. Over 200 earthquakes are recorded each year in the CSZ (Nuttli magnitude, mN \add[OF]{mostly} $\leq$ 3) \citep{Baird_2010} and the hypocenters have a bimodal distribution with peaks at 10 and 22 km depths \citep{Vlahovic_2003}. The vast majority of earthquakes in the CSZ occur within the volume bounded by the rift faults \citep{Yu_2016} and those with greater magnitudes occur northeast of the \change[OF]{crater}{impact structure}~\citep{Mazzotti_2010} (Fig. \ref{figone}).

\begin{figure}[h]
\centering
\includegraphics[width=18.5pc]{Figures/Map_of_CSZ_2.png} 
\caption{Topography\add[OF]{, bathymetry,} and seismicity of the Charlevoix Seismic Zone (CSZ) as well as the locations of the impact \change[OF]{crater}{structure} (outer cyan circle) and the more damaged inner \change[OF]{crater}{impact structure} (inner cyan circle). Small circles \add[OF]{and diamonds} are the relocated epicenters \citep{Powell_2017} \add[OF]{and the complete dataset for the years 1988-2011, respectively,} and their colors represent the focal depths. The focal mechanisms are for the earthquakes used by \citet{Mazzotti_2010} for the stress inversion. Large circles labeled as NW and SE show orientations of SH$_{\max}$ from the stress inversion of focal mechanism (SH$_S$) and from borehole breakout measurements (SH$_B$) for the earthquake clusters northwest and southeast of the \change[OF]{crater}{impact structure} center. Solid black lines mark the rift faults known in the region: GNF, Gouffre Northwest Fault; SLF, Saint-Laurent fault; CHF, Charlevoix Fault; and SSF, South Shore Fault \citep{Rondot_1971,lamontagne1999}. The inset shows the location of the CSZ in eastern Canada. Earthquake \change[OF]{epicenters}{hypocenters} from the National Resources Canada catalog for the years 1988-2011.}
\label{figone}
\end{figure}
